%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Zendesk} % Organization
    {Singapore} % Location
    {Nov. 2023 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained a tool used by >50\% of Zendesk's engineers to maintain their test cases and run it on multiple platform during the development cycle.}
        \item {Integrated the tool mentioned above with multiple Zendesk's internal framework and other tools.}
        \item {Developed a plugin for Zendesk's internal Spinnaker service to run their test cases via Jenkins pipeline during deployment.}
        \item {Handled customer supports to internal users that used the team's tools to increase their productivity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Engineer/Senior Engineer, Web Full Stack} % Job title
  {Sea Ltd. (Previously known as Garena Online Pte. Ltd.)} % Organization
  {Singapore} % Location
  {Jun. 2019 - Nov. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and maintained multiple internal applications using Python (Django) Javascript/Typescript (React), and MySQL.}
      \item {Led and mentored multiple Backend developers in a project to revamp company's procurement system that will improve multiple workflows and better maintainability of the codebase.}
      % \item {Mentored multiple new hires and interns in the team in order for them to understand more on internal tooling and processes in order to be productive and able to contribute to development smoothly.}
      \item {Initiated the idea and development of internal Frontend hooks library (\url{https://coralhooks.insea.io/}) for internal Frontend development purposes.}
      \item {Maintained internal legacy finance systems that handles claims, procurements, and projects for Sea employees; and was able to optimize several operations that costs millions of redundant database calls per hour.}
      \item {Designed and developed a platform for research scientists to search among around 300k research papers (using mini internal search engine built on top of elasticsearch) and subscribe to their searches to receive daily newsletters at their preferred timings.}
      \item {Designed and developed a platform for sales team to engage around 200k Seatalk customers by sending promotional campaigns via email and in-app service notices, while doing real time data-syncing via Kafka with Seatalk in order to do targeted campaigns based on their activity metrics.}
      % \item {Contributed to development of internal Frontend component library (\url{https://coral.insea.io/}) that puts emphasis on accessibility, flexibility, and ease to use by developers.}
      \item {Revamped and maintained web-based real-time data visualization app that enabling metrics analysis for all Sea products that comprises of billions of data rows.}
      \item {Designed and developed central procurement features in order to better control on the company's procurement activities, which contributed to the company's profitability in the tech winter.}
      \item {Initiated official onboarding guidelines for new engineers in the team to have smoother onboarding experience.}
    \end{cvitems}
}

%---------------------------------------------------------
  % \cventry
  % {Engineer, Web Full Stack} % Job title
  % {} % Organization
  % {} % Location
  % {Jun. 2019 - Dec. 2021} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Developed and maintained multiple internal applications using Python (Django) Javascript/Typescript (React), and MySQL.}
  %     \item {Designed and developed a platform for research scientists to search among around 300k research papers (using mini internal search engine built on top of elasticsearch) and subscribe to their searches to receive daily newsletters at their preferred timings.}
  %     \item {Designed and developed a platform for sales team to engage around 200k Seatalk customers by sending promotional campaigns via email and in-app service notices, while doing real time data-syncing via Kafka with Seatalk in order to do targeted campaigns based on their activity metrics.}
  %     \item {Contributed to development of internal Frontend component library (\url{https://coral.insea.io/}) that puts emphasis on accessibility, flexibility, and ease to use by developers.}
  %     \item {Revamped and maintained web-based real-time data visualization app that enabling metrics analysis for all Sea products that comprises of billions of data rows.}
  %     \item {Developed a module for Seatalk OA (\url{https://oa.seatalk.sea.com/}) that allow organisations to create a custom app for their organisations using drag-and-drop functionality.}
  %     \item {Maintained web app for Finance department to update parameters used for revenue statistics for all Sea products and regions.}
  %   \end{cvitems}
  % }

%---------------------------------------------------------
  \cventry
    {Web Application Developer Intern} % Job title
    {Autowealth} % Organization
    {Singapore} % Location
    {May. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web application using HTML/CSS/Javascript (including usage of D3.js and JQuery) for Frontend and PHP for Backend.}
        \item {Developed client dashboard platform for more than 20k clients in order to help them to observe and analyze their investment portfolios, which still on use until this moment.}
        \item {Developed onboarding platform for new clients to help the company onboard the new clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
