%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mobile Developer} % Position
    {Alfred: Boardgame Companion} % Committee
    {} % Location
    {Oct. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In a team of two, developed and launched a companion app using Dart (Flutter) to help boardgamers in order for them to enjoy their games better.}
        \item {Constantly improving and extending the app with new features and games companion.}
        \item {Available on PlayStore: https://play.google.com/store/apps/details?id=lambdaworks.alfredbg}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {iOS Developer} % Position
    {Gooreat Restaurant} % Committee
    {} % Location
    {Mar. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In a team of four, developed a restaurant-themed cooperative game for iOS using Swift (SpriteKit), where players need to cook orders within the time limit in a spaceship.}
        \item {Contributed to the implementation of the game models, logic, and interaction between objects.}
        \item {Won first prize in 14th SoC Terms Project Showcase for CS3217 Final Project}
        \item {Gameplay video: https://www.youtube.com/watch?v=Etk6JAhrhsA}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Position
    {NUSCloud} % Committee
    {} % Location
    {Oct. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In a team of four, developed a web application to help NUS students synchronized their IVLE Workbin (where professors uploaded files for their students) with their personal cloud services (One Drive, Google Drive, Box, and Dropbox).}
        \item {Contributed to the front end part of the app using ReactJS, which call API from the backend and other services and providing good UI/UX to the users.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
